\chapter{ JavaScript Basic }



\chapter{ jQuery }

\chapter{ AngularJS }'

\section{AngularJS Directives}

\begin{enumerate}
    \item  The \textbf{ng-app} directive initializes an AngularJS application. \textbf{The ng-app} directive defines the root element of an AngularJS application.

    \item  The \textbf{ng-init} directive initializes application data.

    \item  The \textbf{ng-model} directive binds the value of HTML controls (input, select, textarea) to application data.
        
    \item  The \textbf{ng-repeat} directive repeats an HTML element:
    
    \item  The \textbf{ng-controller} directive defines the application controller.
    
    \item  The \textbf{ng-if} 
    
    \item The \textbf{ng-disabled} directive binds AngularJS application data to the disabled attribute of HTML elements.
        
    \item The \textbf{ng-show} directive shows or hides an HTML element.
    
    \item The \textbf{ng-click} directive defines an AngularJS click event.
    
    \item With AngularJS, you can include HTML content, using the \textbf{ng-include} directive:
\end{enumerate}

\section{AngularJS Filters}

currency, filter, orderBy, uppercase

\section{Input Validation}

\begin{enumerate}
    \item  \textbf{\textdollar dirty}	The user has interacted with the field.
    \item  \textbf{\textdollar valid}	The field content is valid.
    \item  \textbf{\textdollar invalid}	The field content is invalid.
    \item  \textbf{\textdollar pristine}	User has not interacted with the field yet.
\end{enumerate}

\section{Global  Variables } 

scope, http,  index, odd, even 


\section{AngularJS API}

\begin{enumerate}
    \item angular.lowercase()	Converts a string to lowercase
    \item angular.uppercase()	Converts a string to uppercase
    \item angular.isString()	Returns true if the reference is a string
    \item angular.isNumber()	Returns true if the reference is a number
\end{enumerate}